---
title: "An analysis of the ICA 2020 program"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---


```{r}
require(tidyverse)
require(textclean)
require(quanteda)

ica_raw <- rio::import('70th Annual ICA Conference_29FEB2020.csv') %>% as_tibble
ica_raw
```

```{r}
colnames(ica_raw)
```

I am only interested in a few columns.

```{r}
colnames(ica_raw)[2] <- "event_type"
colnames(ica_raw)[3] <- "event_group"
colnames(ica_raw)[5] <- "start_time"
colnames(ica_raw)[8] <- "event_info"
colnames(ica_raw)[17] <- "abstract"
ica_raw %>% count(event_type) -> all_event_types
### I am only interested in these sessions.
all_event_types[c(5, 6, 7, 8, 9, 11, 14),]
```

```{r, results = 'asis'}
##probably not the cleanest.

ica_raw %>% filter(event_type %in% all_event_types$event_type[c(5, 6, 7, 8, 9, 11, 14)]) %>% mutate(abstract = str_remove(replace_html(abstract), "^Abstracts? ?B?o?d?y?:? ?")) %>% filter(abstract != "") -> ica
ica %>% count(event_group, sort = TRUE) %>% add_count(wt = n, name = "total") %>% mutate(procent = round((n / total) * 100,2)) %>% select(-total) %>% knitr::kable()
```

```{r}
abstract_corpus <- corpus(ica$abstract)
docvars(abstract_corpus, "group") <- ica$event_group
```

```{r}
dfm(abstract_corpus, tolower = TRUE, stem = TRUE, remove_punct = TRUE, remove_symbols = TRUE, remove = stopwords('en')) %>% dfm_select("^[A-Za-z]+$", valuetype = 'regex') -> abstract_dfm
```

Top Features of all ICA abstracts.

```{r}
topfeatures(abstract_dfm, n = 50)
```

# What the "big 10" scholars are writing?

## Health Communication

```{r hc}
textstat_keyness(abstract_dfm, target = docvars(abstract_dfm, "group") == "Health Communication") %>% textplot_keyness
```

## CAT

```{r cat}
textstat_keyness(abstract_dfm, target = docvars(abstract_dfm, "group") == "Communication and Technology") %>% textplot_keyness
```

## JSD

```{r jsd}
textstat_keyness(abstract_dfm, target = docvars(abstract_dfm, "group") == "Journalism Studies") %>% textplot_keyness
```



|Health Communication                                  | 267|    9.93|
|Communication and Technology                          | 232|    8.63|
|Journalism Studies                                    | 199|    7.40|
|Political Communication                               | 192|    7.14|
|Mass Communication                                    | 153|    5.69|
|Information Systems                                   | 141|    5.25|
|Public Relations                                      |  88|    3.27|
|Interpersonal Communication                           |  78|    2.90|
|Computational Methods                                 |  71|    2.64|
|Media Industry Studies                                |  71|    2.64|

